Disentangling the spinal mechanisms of illusory heat and burning sensations in the Thermal Grill Illusion

### 2023-07-12 Manuscript.Rmd
updates

The second experiment showed similar results 
Firstly the cold intensity was less when the cold probe was located more distally for both control and TGI trials (TGI: $\beta$ = `r stats_within_cold_exp2_TGI$beta[2]`, `r make_pvalue(stats_within_cold_exp2_TGI$p[2])`; control: $\beta$ = `r stats_within_cold_exp2_control$beta[2]`, `r make_pvalue(stats_within_cold_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_within_cold_exp2_control$beta[5]`, `r make_pvalue(stats_within_cold_exp2_control$p[5])`. No difference in intensity was found for the warm ratings (TGI: $\beta$ = `r stats_within_warm_exp2_TGI$beta[2]`, `r make_pvalue(stats_within_warm_exp2_TGI$p[2])`; control: $\beta$ = `r stats_within_warm_exp2_control$beta[2]`, `r make_pvalue(stats_within_warm_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_within_warm_exp2_control$beta[5]`, `r make_pvalue(stats_within_warm_exp2_control$p[5])`. significant differences was also found for the burning ratings indicating more distally located cold probe decreased ratings. (TGI: $\beta$ = `r stats_within_burn_exp2_TGI$beta[2]`, `r make_pvalue(stats_within_burn_exp2_TGI$p[2])`; control: $\beta$ = `r stats_within_burn_exp2_control$beta[2]`, `r make_pvalue(stats_within_burn_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_within_burn_exp2_control$beta[5]`, `r make_pvalue(stats_within_burn_exp2_control$p[5])`.

@@

Firstly the cold intensity was less when the cold probe was located more distally for both control and TGI trials (TGI: $\beta$ = `r stats_across_cold_exp1_TGI$beta[2]`, `r make_pvalue(stats_across_cold_exp1_TGI$p[2])`; control: $\beta$ = `r stats_across_cold_exp1_control$beta[2]`, `r make_pvalue(stats_across_cold_exp1_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_cold_exp1_control$beta[5]`, `r make_pvalue(stats_across_cold_exp1_control$p[5])`. No difference in intensity was found for the warm ratings (TGI: $\beta$ = `r stats_across_warm_exp1_TGI$beta[2]`, `r make_pvalue(stats_across_warm_exp1_TGI$p[2])`; control: $\beta$ = `r stats_across_warm_exp1_control$beta[2]`, `r make_pvalue(stats_across_warm_exp1_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_warm_exp1_control$beta[5]`, `r make_pvalue(stats_across_warm_exp1_control$p[5])`. significant differences was also found for the burning ratings indicating more distally located cold probe decreased ratings. (TGI: $\beta$ = `r stats_across_burn_exp1_TGI$beta[2]`, `r make_pvalue(stats_across_burn_exp1_TGI$p[2])`; control: $\beta$ = `r stats_across_burn_exp1_control$beta[2]`, `r make_pvalue(stats_across_burn_exp1_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_burn_exp1_control$beta[5]`, `r make_pvalue(stats_across_burn_exp1_control$p[5])`.

The second experiment showed similar results 
Firstly the cold intensity was less when the cold probe was located more distally for both control and TGI trials (TGI: $\beta$ = `r stats_across_cold_exp2_TGI$beta[2]`, `r make_pvalue(stats_across_cold_exp2_TGI$p[2])`; control: $\beta$ = `r stats_across_cold_exp2_control$beta[2]`, `r make_pvalue(stats_across_cold_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_cold_exp2_control$beta[5]`, `r make_pvalue(stats_across_cold_exp2_control$p[5])`. No difference in intensity was found for the warm ratings (TGI: $\beta$ = `r stats_across_warm_exp2_TGI$beta[2]`, `r make_pvalue(stats_across_warm_exp2_TGI$p[2])`; control: $\beta$ = `r stats_across_warm_exp2_control$beta[2]`, `r make_pvalue(stats_across_warm_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_warm_exp2_control$beta[5]`, `r make_pvalue(stats_across_warm_exp2_control$p[5])`. significant differences was also found for the burning ratings indicating more distally located cold probe decreased ratings. (TGI: $\beta$ = `r stats_across_burn_exp2_TGI$beta[2]`, `r make_pvalue(stats_across_burn_exp2_TGI$p[2])`; control: $\beta$ = `r stats_across_burn_exp2_control$beta[2]`, `r make_pvalue(stats_across_burn_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_burn_exp2_control$beta[5]`, `r make_pvalue(stats_across_burn_exp2_control$p[5])`.

@@

# Authors contributions
Author contributions listed alphabetically according to [CRediT taxonomy](https://credit.niso.org):
Conceptualization: DEC, JFE, FF, PH, AGM.
Data curation: JEF, AGM.
Formal analysis: JFE, FF, AGM.
Funding acquisition: FF.
Investigation: DEC, JFE, AGM.
Methodology: DEC, JFE, FF, AGM, AVS.
Project administration: FF, AGM.
Resources: FF, AGM.
Software: JFE, FF, AGM.
Supervision: FF, AGM.
Visualization: FF, AGM.
Writing – original draft: FF, AGM.
Writing – review & editing: FF, AGM. (+ others who will provide feedback)

>>>>

The second experiment showed no difference that the cold intensity was less when the cold probe was located more distally for both control and TGI trials (TGI: $\beta$ = `r stats_within_cold_exp2_TGI$beta[2]`, `r make_pvalue(stats_within_cold_exp2_TGI$p[2])`; control: $\beta$ = `r stats_within_cold_exp2_control$beta[2]`, `r make_pvalue(stats_within_cold_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_within_cold_exp2_control$beta[5]`, `r make_pvalue(stats_within_cold_exp2_control$p[5])`. No difference in intensity was found for the warm ratings (TGI: $\beta$ = `r stats_within_warm_exp2_TGI$beta[2]`, `r make_pvalue(stats_within_warm_exp2_TGI$p[2])`; control: $\beta$ = `r stats_within_warm_exp2_control$beta[2]`, `r make_pvalue(stats_within_warm_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_within_warm_exp2_control$beta[5]`, `r make_pvalue(stats_within_warm_exp2_control$p[5])`. No significant differences was also found for the burning ratings for both TGI and control. (TGI: $\beta$ = `r stats_within_burn_exp2_TGI$beta[2]`, `r make_pvalue(stats_within_burn_exp2_TGI$p[2])`; control: $\beta$ = `r stats_within_burn_exp2_control$beta[2]`, `r make_pvalue(stats_within_burn_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_within_burn_exp2_control$beta[5]`, `r make_pvalue(stats_within_burn_exp2_control$p[5])`.

@@

Firstly the cold intensity was more when the cold probe was located more rostrally for both control and TGI trials  (TGI: $\beta$ = `r stats_across_cold_exp1_TGI$beta[2]`, `r make_pvalue(stats_across_cold_exp1_TGI$p[2])`; control: $\beta$ = `r stats_across_cold_exp1_control$beta[2]`, `r make_pvalue(stats_across_cold_exp1_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_cold_exp1_control$beta[5]`, `r make_pvalue(stats_across_cold_exp1_control$p[5])`. A significant reduction in warm intensity was found for TGI trials, but not for the control trials (TGI: $\beta$ = `r stats_across_warm_exp1_TGI$beta[2]`, `r make_pvalue(stats_across_warm_exp1_TGI$p[2])`; control: $\beta$ = `r stats_across_warm_exp1_control$beta[2]`, `r make_pvalue(stats_across_warm_exp1_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_warm_exp1_control$beta[5]`, `r make_pvalue(stats_across_warm_exp1_control$p[5])`. No significant differences was found for the burning ratings.(TGI: $\beta$ = `r stats_across_burn_exp1_TGI$beta[2]`, `r make_pvalue(stats_across_burn_exp1_TGI$p[2])`; control: $\beta$ = `r stats_across_burn_exp1_control$beta[2]`, `r make_pvalue(stats_across_burn_exp1_control$p[2])`) with no significant interaction between them  ($\beta$ = `r stats_across_burn_exp1_control$beta[5]`, `r make_pvalue(stats_across_burn_exp1_control$p[5])`).

The second experiment showed that the cold intensity was more when the cold probe was located more rostrally for TGI trials, but not control trials. (TGI: $\beta$ = `r stats_across_cold_exp2_TGI$beta[2]`, `r make_pvalue(stats_across_cold_exp2_TGI$p[2])`; control: $\beta$ = `r stats_across_cold_exp2_control$beta[2]`, `r make_pvalue(stats_across_cold_exp2_control$p[2])`) with a significant interaction between them  $\beta$ = `r stats_across_cold_exp2_control$beta[5]`, `r make_pvalue(stats_across_cold_exp2_control$p[5])`. A significant difference in intensity was found for the warm ratings indicating that when the cold probe was located more rostrally the intensity was lower (TGI: $\beta$ = `r stats_across_warm_exp2_TGI$beta[2]`, `r make_pvalue(stats_across_warm_exp2_TGI$p[2])`; control: $\beta$ = `r stats_across_warm_exp2_control$beta[2]`, `r make_pvalue(stats_across_warm_exp2_control$p[2])`) with no significant interaction between them  $\beta$ = `r stats_across_warm_exp2_control$beta[5]`, `r make_pvalue(stats_across_warm_exp2_control$p[5])`. A significant differences was also found for the burning ratings in the control condition, but not in the TGI condition, indicating more distally located cold probe decreased ratings in the control condition. (TGI: $\beta$ = `r stats_across_burn_exp2_TGI$beta[2]`, `r make_pvalue(stats_across_burn_exp2_TGI$p[2])`; control: $\beta$ = `r stats_across_burn_exp2_control$beta[2]`, `r make_pvalue(stats_across_burn_exp2_control$p[2])`) with no significant interaction between them  ($\beta$ = `r stats_across_burn_exp2_control$beta[5]`, `r make_pvalue(stats_across_burn_exp2_control$p[5])`).

@@

# Authors contributions
Author contributions listed alphabetically according to [CRediT taxonomy](https://credit.niso.org):

-   Conceptualization: DEC, JFE, FF, PH, AGM.
-   Data curation: JEF, AGM.
-   Formal analysis: JFE, FF, AGM.
-   Funding acquisition: FF.
-   Investigation: DEC, JFE, AGM.
-   Methodology: DEC, JFE, FF, AGM, AVS.
-   Project administration: FF, AGM.
-   Resources: FF, AGM.
-   Software: JFE, FF, AGM.
-   Supervision: FF, AGM.
-   Visualization: FF, AGM.
-   Writing – original draft: FF, AGM.
-   Writing – review & editing: FF, AGM. (+ others who will provide feedback)
